Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies

### 2018-09-04 ms.tex
removed one word from asbtract
typo and acknowledgement fix

\begin{abstract}
%
%
% NOTE: Overleaf includes abstract words in word count in text... subtract
%       this from the total.
%
%
Effective stellar feedback is used in models of galaxy formation to regulate star formation and drive realistic galaxy evolution. Models typically include energy injection from supernovae as the dominant form of stellar feedback, often in some form of sub-grid recipe. However, it has been recently suggested that pre-SN feedback (stellar winds or radiation) is necessary in high-resolution simulations of galaxy evolution to properly regulate star formation and properties of the interstellar medium (ISM). However, following these processes is computationally challenging, 
%Following stellar winds and ionizing radiation is computationally challenging, 
so many prescriptions model this feedback approximately, accounting for the local destruction of dense gas clouds around newly formed stars in lieu of a full radiative transfer calculation. In this work we examine high resolution simulations (1.8~pc) of an isolated dwarf galaxy with detailed stellar feedback tracked on a star-by-star basis. By following stellar ionizing radiation with an adaptive ray-tracing radiative transfer method, we test its importance in regulating star formation and driving outflows in this galaxy. We find that including ionizing radiation reduces the star formation rate (SFR) by over a factor of 5, and is necessary in creating the ISM conditions needed for supernovae to drive significant outflows. We find that a localized approximation for radiation feedback is sufficient to regulate the SFR on short timescales, but is unable to drive significant outflows. Short and long range radiation effects are both important in driving the evolution of our \textbf{low-metallicity, low-mass dwarf galaxy. Generalization of these results to more massive galaxies would be a valuable avenue of future research.}
\end{abstract}

@@

\textbf{These results show that long-range ionization effects are an important consideration in models of stellar feedback. However, it warrants further study as to how much this effect can be accounted for without resorting to full radiative transfer calculations. Approximate, Stromgren-like feedback models which allow for ionization far from a single source \citep[e.x.][]{Hopkins2018} may be sufficient to capture the effects shown here. Fully localized methods, or methods which set a maximum for the ionization radius may underestimate galactic wind properties in dwarf galaxies. However, both methods are mass biased \citep[see the discussion in ][]{Hu2017}, preferentially over-ionizing dense gas that would otherwise be missed by photons leaking through channels carved through lower-density gas. These remaining uncertainties motivate a continued examination of the feedback prescriptions adopted in high resolution simulations of galaxy evolution.}

@@

\acknowledgments
A.E. is funded by the NSF Graduate Research Fellowship DGE 16-44869. G.L.B. is funded by NSF AST-1312888, NASA NNX15AB20G, and NSF AST-1615955. M.-M.M.L. was partly funded by NASA  grant NNX14AP27G and NSF grant AST18-15461. We gratefully recognize computational resources provided by NSF XSEDE through grant number TGMCA99S024, the NASA High-End Computing Program through the NASA Advanced Supercomputing Division at Ames Research Center, Columbia University, and the Flatiron Institute. This work made significant use of many open source software packages, including \textsc{yt}, \textsc{Enzo}, \textsc{Grackle}, \textsc{Python}, \textsc{IPython}, \textsc{NumPy}, \textsc{SciPy}, \textsc{Matplotlib}, \textsc{HDF5}, \textsc{h5py}, \textsc{Astropy}, \textsc{Cloudy} and \textsc{deepdish}. These are products of collaborative effort by many independent developers from numerous institutions around the world. Their commitment to open science has helped make this work possible.

>>>>

\begin{abstract}
%
%
% NOTE: Overleaf includes abstract words in word count in text... subtract
%       this from the total.
%
%
Effective stellar feedback is used in models of galaxy formation to 
%regulate star formation and 
drive realistic galaxy evolution. Models typically include energy injection from supernovae as the dominant form of stellar feedback, often in some form of sub-grid recipe. However, it has been recently suggested that pre-SN feedback (stellar winds or radiation) is necessary in high-resolution simulations of galaxy evolution to properly regulate star formation and properties of the interstellar medium (ISM). However, following these processes is computationally challenging, 
%Following stellar winds and ionizing radiation is computationally challenging, 
so many prescriptions model this feedback approximately, accounting for the local destruction of dense gas clouds around newly formed stars in lieu of a full radiative transfer calculation. In this work we examine high resolution simulations (1.8~pc) of an isolated dwarf galaxy with detailed stellar feedback tracked on a star-by-star basis. By following stellar ionizing radiation with an adaptive ray-tracing radiative transfer method, we test its importance in regulating star formation and driving outflows in this galaxy. We find that including ionizing radiation reduces the star formation rate (SFR) by over a factor of 5, and is necessary in creating the ISM conditions needed for supernovae to drive significant outflows. We find that a localized approximation for radiation feedback is sufficient to regulate the SFR on short timescales, but is unable to drive significant outflows. Short and long range radiation effects are both important in driving the evolution of our \textbf{low-metallicity, low-mass dwarf galaxy. Generalization of these results to more massive galaxies would be a valuable avenue of future research.}
\end{abstract}

@@

\textbf{These results show that long-range ionization effects are an important consideration in models of stellar feedback. However, it warrants further study as to how much this effect can be accounted for without resorting to full radiative transfer calculations. Approximate, Str{\"o}mgren-like feedback models which allow for ionization far from a single source \citep[e.g.][]{Hopkins2018} may be sufficient to capture the effects shown here. Fully localized methods, or methods which set a maximum for the ionization radius may underestimate galactic wind properties in dwarf galaxies. In addition, both methods are mass biased \citep[see the discussion in ][]{Hu2017}, preferentially over-ionizing dense gas that would otherwise be missed by photons leaking through channels carved through lower-density gas. These remaining uncertainties motivate a continued examination of the feedback prescriptions adopted in high resolution simulations of galaxy evolution.}

@@

\acknowledgments
A.E. is funded by the NSF Graduate Research Fellowship DGE 16-44869. G.L.B. acknowledges support from NSF AST-1312888, NASA NNX15AB20G, and NSF AST-1615955. M.-M.M.L. was partly funded by NASA  grant NNX14AP27G and NSF grant AST18-15461. We gratefully recognize computational resources provided by NSF XSEDE through grant number TGMCA99S024, the NASA High-End Computing Program through the NASA Advanced Supercomputing Division at Ames Research Center, Columbia University, and the Flatiron Institute. This work made significant use of many open source software packages, including \textsc{yt}, \textsc{Enzo}, \textsc{Grackle}, \textsc{Python}, \textsc{IPython}, \textsc{NumPy}, \textsc{SciPy}, \textsc{Matplotlib}, \textsc{HDF5}, \textsc{h5py}, \textsc{Astropy}, \textsc{Cloudy} and \textsc{deepdish}. These are products of collaborative effort by many independent developers from numerous institutions around the world. Their commitment to open science has helped make this work possible.
